---
title: "assign4"
output: html_notebook
---
```{r}
#import library
library(tidyverse)
library(devtools)
library(RVerbalExpressions)
library(lubridate)
```


For the regular expression exercises, try writing first using regular expressions directly, then try using rverbalexpressions. Provide the code for both. 

# Part 1

## R4DS 16.4.5

Create a vector of dates giving the first day of every month in the current year. 
```{r}
floor_date(today(), unit = "year")+ months(0:11)
```



Write a function that given your birthday (as a date), returns how old you are in years.
```{r}
age <- function(x){
  year(today())-year(ymd(x))
}

age(19971008)
```


Write a function that given your birthday, returns the day of the week you were born on. 
```{r}
bornweek <- function(x){
  wday(ymd(x),label = TRUE)
}

bornweek(19971008)
```

## R4DS 14.3.2.1

Given the corpus of common words in stringr::words, create regular expressions that find all words that have seven letters or more. (Since this list is long, you might want to use the match argument to str_view() to show only the matching or non-matching words.)
```{r}
words <- stringr::words

# regular expressions
str_view(words,"^\\w{7,}$",match = TRUE)
```
```{r}
# verbal expressions
seven_or_more <- rx()%>%
  rx_start_of_line()%>%
  rx_word_char()%>%
  rx_repeat_previous(7)%>%
  rx_anything()%>%
  rx_end_of_line()%>%
  print()

str_view(words,seven_or_more,match = TRUE)
```



## R4DS 14.3.3.1

Use str_detect to find all words that:

That only contain consonants. (Hint: thinking about matching “not”-vowels.)
```{r}
# verbal expression
words[str_detect(words,"^[^aeiou]+$")]

# regular expression
consonants <- rx() %>% 
  rx_start_of_line() %>% 
  rx_something_but("aeiou") %>% 
  rx_end_of_line()%>%
  print()

words[str_detect(words, consonants)]
```

Empirically verify the rule “i before e except after c”.
```{r}
# verbal expression
words[str_detect(words, "[^c]ie")]

# regular expression
rule <- rx() %>% 
  rx_something_but("c") %>% 
  rx_find("i") %>% 
  rx_find("e") %>% 
  print()
words[str_detect(words, rule)]
```

Create a regular expression that will match telephone numbers as commonly written in the US. Split this up into multiple expressions as needed.
```{r}
# regular expression
telephonerx <- rx() %>%
  rx_start_of_line() %>%
  rx_maybe("(") %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_maybe(")") %>% 
  rx_any_of("-. ") %>% 
  rx_digit() %>% 
  rx_repeat_previous(3) %>% 
  rx_any_of("-. ") %>%
  rx_digit() %>% 
  rx_repeat_previous(4) %>% 
  rx_end_of_line() %>% 
  print() %>% 
  grepl(c("217-377-2867", "217.377.2867", "EM7.377.2867","(912) 356 4327")) %>% 
  print()
```

# Part 2


Choose a dataset (this can be the same dataset as the last assignment, or a new one). Define a predictive modeling problem. Create the appropriate files and notebooks to do the following:

1. Describe the data and the problem

2. Read in and check data

2. Clean up the data. 

*Note: You may request that score for these sections replace your score for the coding portion of Assignment 3.*

4. Using best practices, write four functions which add engineered features to the dataset, including a description and rationale. Include a test to determine whether the features are working as intended. 

5. Prepare the data for modeling

Note: this will form the basis for your midterm project. Take advantage of TA's and my office hours. We can provide feedback and guidance. 

